%!TEX root = ../RASD/main.tex
\section{Overall Description}
\subsection{Product Perspective}
As stated in the \emph{\nameref{sub:scope}} section the product we will release is composed by four main software applications.
\begin{itemize}
  \item A \textbf{Web Application (User)} addressed to the \emph{users}  to use our service. This application must interface mainly with the \textbf{Back-end Application} and with Google's Maps API.
  \item A \textbf{Mobile Application (User)} addressed to the \emph{users} to use our service and available for Android, iOS, Windows Mobile and Blackberry. This application must interface mainly with our \textbf{Back-end Application} and with Google's Maps API
  \item A \textbf{Mobile Application (Taxi Driver)} addressed to the \emph{taxi drivers} to use our service and available for Android, iOS. This application must interface mainly with our \textbf{Back-end Application} and with Google's Maps API

  \item A \textbf{Back-end Application} that will handle all the business logic and that must interface mainly with Google's Maps API and with a MongoDB database .
\end{itemize}

\subsubsection{User Interfaces}
%to complete
\subsubsection{Hardware Interfaces}
Both the \emph{Mobile Application (User)} and the \emph{Mobile Application (Taxi Driver)} must interface with the GPS module and with the Network module.\\

\subsubsection{Software Interfaces}


\paragraph{Web Application (User)} 

\begin{itemize}
	\item MyTaxyService API
	\begin{itemize}
		\item Mnemonic : Back-end
	\end{itemize}
	\item Google Maps API
	\begin{itemize}
		\item Mnemonic : Google Maps API
		\item Version Number : V3
		\item Source : \url{https://developers.google.com/maps/documentation/javascript/} 
	\end{itemize}

\end{itemize}

\paragraph{Mobile Application (User and Taxi Driver)} 
\begin{itemize}
	\item MyTaxyService API
	\begin{itemize}
		\item Mnemonic : Back-end
	\end{itemize}
	\item Google Maps API
	\begin{itemize}
		\item Mnemonic : Google Maps API
		\item Version Number : V3
		\item Source : \url{https://developers.google.com/maps/} 
	\end{itemize}

	\item Android SDK
	\begin{itemize}
		\item Mnemonic : Android
		\item Version Number : 6.0
		\item Source : \url{http://developer.android.com/sdk/index.html} 
	\end{itemize}

	\item iOS SDK
	\begin{itemize}
		\item Mnemonic : iOS
		\item Version Number : 9.2
		\item Source : \url{https://developer.apple.com/ios/download/} 
	\end{itemize}

	\item Windows Mobile SDK
	\begin{itemize}
		\item Mnemonic : Windows Mobile
		\item Version Number : 6.5
		\item Source : \url{http://www.microsoft.com/en-us/download/details.aspx?id=17284} 
	\end{itemize}

	\item BlackBerry SDK
	\begin{itemize}
		\item Mnemonic : BlackBerry
		\item Version Number : 10
		\item Source : \url{https://developer.blackberry.com/} 
	\end{itemize}		
\end{itemize}

\paragraph{Back-end Application} 

\begin{itemize}
	\item Node.js API
	\begin{itemize}
		\item Mnemonic : Node.js
		\item Version : 4.2.1
		\item Source : \url{https://nodejs.org/api/}
	\end{itemize}

	\item MongoDB API
	\begin{itemize}
		\item Mnemonic : MongoDB
		\item Version : 3.0
		\item Source : \url{https://docs.mongodb.org/manual/}
	\end{itemize}

	\item Google Maps API
	\begin{itemize}
		\item Mnemonic : Google Maps API
		\item Version Number : V3
		\item Source : \url{https://developers.google.com/maps/documentation/javascript/}
	\end{itemize}
	\item Javascript API
	\begin{itemize}
		\item Mnemonic : Javascript
		\item Source : \url{https://developer.mozilla.org/en/docs/Web/API} 
	\end{itemize}
\end{itemize}

\subsubsection{Communication Interfaces} 
\label{ssub:communication_interfaces}
\paragraph{Web Application (User)}\mbox{} \\
Every application must interface with the Internet network. This interface is handled by the operative systems and not by The applications themselves.

\subsubsection{Memory Constrains} 

\label{ssub:memory_constrains}
\paragraph{Mobile Applications (User and Taxi Driver) and Web Application}
The Mobile and Web Applications can not exceed 75MB of RAM usage.
\paragraph{Back-End Application}
The Back-End application can not exceed 15GB of total RAM usage.

\subsubsection{Site Adaptation Requirements} 
\label{ssub:site_adaptation_requirements}
\paragraph{Software Adaptation} \mbox{} \\
Every Mobile Application must be developed according to the platforms design guidelines.

\subsection{Product Functions} 
\label{sub:product_functions}
This section highlights the main product functions sorted by application.

\subsubsection{Web Application and Mobile Application (User)}
\label{ssub:web_application_and_mobile_application_}
\begin{enumerate} [label = \textbf{[F\arabic*]}]
	\item  The app must allow the user to book a taxi on the spot.
	\item  The app must allow the user to reserve a taxi ride up to 7 days before the chosen date.
	\item  The app must allow the user to share his ride with other people whose destination is included in the ride path.
\end{enumerate}

\subsubsection{Mobile Application (Taxi Driver)} 
\label{ssub:mobile_application_}
\begin{enumerate} [resume*]
	\item  The app must provide position updates to the \emph{back-end application}
	\item  The app must allow the taxi driver to accept or refuse a ride request.
	\item  The app must allow the taxi driver to report issues that could delay his arrival (traffic jam, car faults, etc ...)
	\item  The app must allow the taxi driver to overview a history of his last rides.
	\item  The app must allow the taxi driver to report a absent user.
\end{enumerate}

\subsubsection{Back-End Application} 
\label{ssub:back_end_application}
\begin{enumerate} [resume*]
	\item  The application must provide an interface for the registration process of users and taxi drivers
	\item  The application must handle the request queue using a fair policy [Rif needed]
	\item  The application must provide an accurate [rif needed] estimate of the total cost and time of a ride
	\item  The application must provide an interface to allow an operator to perform all basics CRUD operations

\end{enumerate}

\subsection{User Characteristics} 
\label{sub:user_characteristics}
This section identifies all the different users of the product.
\paragraph{User}\label{par:user} [rif needed] The user has to be at least 13 years old.\\ 
Has to be familiar with standard mobile applications interfaces.
\paragraph{Taxi Driver}\label{par:taxy_driver} [rif needed] The driver has to be a regularly licensed taxi driver.\\ The driver has to be familiar with standard mobile applications interfaces and is required to own a compatible device [rif needed]
\paragraph{Maintenance Guy} \label{par:maintenance_guy}
[rif needed] The maintenance guy must be able to debug and identify issues in a full stack environment. The maintenance guys must be familiar with the application requirements and the overall infrastructure and design.
\paragraph{Support Operator} \label{par:support_operator} The support operator must be familiar with the overall application design and has to know how to resolve common user's issues.

\subsection{Constraints} 
\label{sub:constraints}

\subsubsection{Regulatory Policies} 
\label{ssub:regulatory_policies}
\begin{itemize}
	\item \textbf{Privacy Policy} Data should be collected and stored following the privacy policy guidelines provided by Mozzilla Foundation [rif needed] 	\url{https://developer.mozilla.org/en-US/Marketplace/Publishing/Policies_and_Guidelines/Privacy_policies}
	\item \textbf{Taxi Driver Policy} The client application for taxi drivers must be accessible only by registered and regularly licensed driver.[rif neeeded]
\end{itemize}

\subsubsection{Hardware Limitations} 
\label{ssub:hardware_limitations}
\paragraph{Mobile Application (User)} 
The Mobile Application (User) must be developed in order to be available for the 80\% of the devices currently on the market for each different platform.
\paragraph{Web Application (User)}
The Web Application must be developed in order to be available for the 100\% of devices that support the latest version [rif needed] of most used browser [rif needed]


\subsubsection{Interfaces to other applications} 
\label{ssub:interfaces_to_other_applications}
\paragraph{Mobile Application (User)} 
\label{par:mobile_application_}
The developer of the Mobile Application (User) must follow the design guideline [rif needed ] of the platform and has to interface with the respective Developer Console and make sure that the app will be accepted and published. \\
The application must interface with Google's Maps API [rif needed].
\paragraph{Web Application (User)} 
The application must interface with Google's Maps API [rif needed].
\paragraph{Mobile Application (Taxi Driver)} 
The application must interface with Google's Maps API [rif needed].
\paragraph{Back-end Application} 
The application must interface with Google's Maps API [rif needed].

\subsubsection{Parallel Operations} 
\label{ssub:parrallel_operations}
\paragraph{Back-end Application} 
The Back-end Application must handle parallel request from multiple users without generating conflicts or inconsistency.\\
The system must decline a request from a user if it finds another active request from the same user.

\subsubsection{Reliability Requirements} 
\label{ssub:reliability_requirements}
\paragraph{Back-end Application} 
This requirement of reliability and availability refers to the total time the system is available for the applications of the end users.\\
The system must reach a 99.99\% uptime (corresponding to a inactivity time of 50 minutes/year).
\subsubsection{Safety and Security} 
\label{ssub:safety_and_security}
\paragraph{Mobile Application (Taxi Driver)} 
The application must include an automatic night mode and gallery mode in order not to compromise the driver security [rif needed]

\subsection{Assumptions And Dependencies} 
\label{sub:assumptions_and_dependencies}
\subsubsection{Domain Assumptions} 
\label{ssub:domain}
We assume that the system will be deployed in a city of about 1.5M inhabitants with about 4800 regular licensed taxi drivers.\\
We assume that at launch time the end user mobile application will reach an audience of about 100k users while the web application will reach an audience of about 10k users.\\
We assume that the city is dived in taxi zones.
\subsubsection{Taxi Driver Assumptions} 
We assume that every taxi driver will have a compatible device (personal or provided by the project client) [rif needed] with a working GPS module.
\subsubsection{User Assumptions} 
\label{ssub:user_assumptions}
We assume that every user will have a device with an enabled Internet connection.\\
We also assume that the location provided by the user (manually or automatically via GPS) is always correct.